Milk intake and risk of mortality risk

### 2020-06-15 Paperfolder/Paperfolder.Rmd
updated with new tables

>>>>

```{r tab1, echo=FALSE, eval=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
dt <- read.csv("tab/HRAFTweib.csv", header = T)
names(dt) <- c("Milk intake", "Median", "Mean (SD)", "95% CrI", "MCSE", "Probability", "Median", "Mean (SD)", "95% CrI", "MCSE")
kable(dt, format = "latex", caption = "", booktabs = T,linesep = "") %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
  add_header_above(c(" ", "Hazard ratio (HR)" = 5, "Acceleration factor (AF)" = 4)) %>% 
  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Probability indicates that the p for HR smaller than 1."))
```

### 2020-06-15 Paperfolder/Paperfolder.tex
updated with new tables

Authors should discuss the results and how they can be interpreted in
perspective of previous studies and of the working hypotheses. The
findings and their implications should be discussed in the broadest
context possible. Future research directions may also be highlighted.

@@

This section is not mandatory, but can be added to the manuscript if the
discussion is unusually long or complex.

@@

%=====================================
% References, variant B: external bibliography
%=====================================
\reftitle{References}
\externalbibliography{yes}
\bibliography{mybibfile.bib}

>>>>

@@

@@

%=====================================
% References, variant B: external bibliography
%=====================================
\reftitle{References}
\externalbibliography{yes}
\bibliography{milk.bib}
